### 2017-10-13 Gruba/02-overview.tex

\begin{figure}[tb!]
\centering
\includegraphics[width=.75\linewidth]{figures/architecture.pdf}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

>>>>

\begin{figure}[tb!]
\centering
\includegraphics[width=.7\linewidth]{figures/architecture.pdf}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\stitle{Sina Microblog Data.} It is the data to be processed by \sys{}, i.e., data of microblogs and users, as shown in \textit{Definitions} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

### 2017-10-13 Gruba/03-fe.tex

\begin{table}[!htb]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{variable}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
\multirow{4}{*}{$R_{ee}$} & \multirow{2}{*}{a ratio defined as the number of followers} \\
                   &                     \\
                   & \multirow{2}{*}{over that of followees, i.e., $\frac{\#R_u}{\#E_u}$} \\
                   & 						\\	\midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{value}} & \multicolumn{1}{c}{\textbf{illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ \& \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

>>>>

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\  
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}
